Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-13 chapters/introduction/introduction.tex
introduction changes

\section{\todo{Dataset}}
Introduce the dataset we use.

@@

  \item \textbf{Constraint for Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the camera geographic
  location with the input image.
  We provide two approaches to obtain the probability distribution over the camera
  geographic location. Most straightforwardly, our network estimate the
  categorical distribution over world into a $N \times M$ bins. Better
  results can be procured with temporal inputs (image timestamps).
  Our algorithm can also compute the probability at arbitrary
  geographic location, with lower accuracy than the straightforward
  method.
  We demonstrate that our algorithm is able to learn geo-temporal
  image representations with geographic locations and capture
  time.
  We present the algorithm details in \chapref{whenwhere}.
  \newline

@@

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Feature Learning}
  Current machine learning methods address problems that involves mostly
  the ground-level imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery. In
  \chapref{crosstransf}, we proposed a method to learn aerial image
  semantic segmentation with ground-level ground truth. Our method
  exploits the spatial correspondences between images in cross-view
  pairs. 
  In this work, we try to transfer the semantics from the ground
  imagery to the overhead imagery by identifying the latent geometry
  correspondences between these two.  Similar to the monocular depth
  estimation methods that driven by the technique called {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the overhead
  images to the ground images, and to segment the overhead images
  jointly.

  \item \textbf{Geo-Temporal Feature Learning}
  In our work, we consider two novel pretext
  tasks, time and location estimation. Our work is most similar to Li
  and Snavely~\cite{li2018learning}, who propose an approach for
  learning intrinsic images by observing image sequences with varying
  illumination over time. While their targets are reflectance and
  shading images of the scene, we focus on location and time.
\end{itemize}

>>>>

%\section{\todo{Dataset}}
%Introduce the dataset we use.

@@

  \item \textbf{Constraint for Time and Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the capture time and the
  camera geographic location with the input image.
  Our network has two branches to predict the image capture time and
  the geographic location jointly.
  For time estimation, our network is able to predict the
  distribution over the month of the year and the global hour of the
  day when the input image has been captured.
  For camera geo-localization, We provide two approaches to obtain the
  probability distribution over the camera geographic location. Most
  straightforwardly, our network estimate the categorical distribution
  over world into a $N \times M$ bins. Better results can be procured
  with temporal inputs (image timestamps).  Our algorithm can also
  compute the probability at arbitrary geographic location, with lower
  accuracy than the straightforward method.
  We present the algorithm details in \chapref{whenwhere}.
  \newline

@@

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Feature Learning:}
  Current machine learning methods address problems that involves mostly
  the ground-level imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery. In
  \chapref{crosstransf}, we proposed a method to learn aerial image
  semantic segmentation with ground-level ground truth. Our method
  exploits the spatial correspondences between images in cross-view
  pairs. 
  In this work, we try to transfer the semantics from the ground
  imagery to the overhead imagery by identifying the latent geometry
  correspondences between these two.  Similar to the monocular depth
  estimation methods that driven by the technique called {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the overhead
  images to the ground images, and to segment the overhead images
  jointly.
  \newline

  \item \textbf{Geo-Temporal Feature Learning:}
  In \chapref{whenwhere}, we demonstrate that our algorithm is able to
  learn geo-temporal image representations with geographic locations and
  capture time.
  Our work is most similar to Li and Snavely~\cite{li2018learning},
  who propose an approach for learning intrinsic images by observing
  image sequences with varying illumination over time. While their
  targets are reflectance and shading images of the scene, we consider
  two novel pretext tasks, time and location estimation.
  By learning to predict its geographic location and capture time from the
  query image, our network learns to extract geo-temporal features
  from the image.
